### 2010-07-09 code/subarchitectures/visualization.sa/trunk/doc/v11n.tex
v11n: docs

The display server can present HTML forms and send data from a form to a client
when the form is submitted. The data from a form can also be saved into a
persistent storage and reloaded later. This way the forms can be used to
configure the components from the user interface instead of using CAST
configuration files.
%
\todo{TODO: Apply the settings from persistent storage at startup when a component
registers a form}
%
\todo{TODO: Add config param to DS to change the location of persistent storage}
%
\todo{TODO: Add menu entry to change the location of persistent storage}
%
\todo{TODO: Add widgets to load/save all forms on a page}

>>>>

The display server can present HTML forms and send data from a form to a client
when the form is submitted. The data from a form can also be saved into a
persistent storage and reloaded later. This way the forms can be used to
configure the components from the user interface instead of using CAST
configuration files.
